\begin{SongText}[The Scotsman's Kilt]
    \begin{SongVerse}
        Well, a Scotsman clad in kilt left a bar one evening fair,\\*%
        and one could tell by how he walked that he'd drunk more than his shared.\\*%
        He fumbled 'round until he could no longer keep his feet,\\*%
        and he stumbled off into the grass to sleep beside the street.
    \end{SongVerse}
    \begin{SongVerse}
        Ring-ding diddle-iddle-i-dee-o, Ring di diddle-i-o
        and he stumbled off into the grass to sleep beside the street.
    \end{SongVerse}
    \begin{SongVerse}
        About that time two young and lovely girls just happened by,\\*%
        One says to the other with a twinkle in her eye:\\*%
        "See a sleeping Scotsman, so strong and handsome built,\\*%
        I wonder if it's true what they don't wear beneath the kilt!"
    \end{SongVerse}
    \begin{SongVerse}
        Ring...\\*%
        I wonder if it's true what they don't wear beneath the kilt!"
    \end{SongVerse}
    \begin{SongVerse}
        They crept up on that sleeping Scotsman quiet as could be;\\*%
        lifted up his kilt about an inch so they could see.\\*%
        And there, behold, for them to view beneath his Scottish skirt,\\*%
        was nothin' more than God had graced him with upon his birth. \\*%
        Ring...\\*%
        was nothing' more than God had graced him with upon his birth.
    \end{SongVerse}
    \begin{SongVerse}
        They marvelled for a moment, then one said: "We must be gone.\\*%
        Let's leave a present for our friend before we move along."\\*%
        As a gift they left a blue silk ribbon tied into a bow,\\*%
        around the bonnie star the Scotsman's kilt did lift and show.
    \end{SongVerse}
    \begin{SongVerse}
        Ring...\\*%
        around the bonnie star the Scotsman's kilt did lift and show.
    \end{SongVerse}
    \begin{SongVerse}
        Now the Scotsman woke to nature's call, and stumbled towards the trees.\\*%
        Behind the bush he lifts his kilt, and gawks at what he sees.\\*%
        And in a startled voice he says, to what's before his eyes,\\*%
        "Oh, lad I don't know where ye been, but I see ye won first prize!"
    \end{SongVerse}
    \begin{SongVerse}
        Ring...\\*%
        "Oh, lad I don't know where ye been, but I see ye won first prize!"
    \end{SongVerse}
    \begin{SongVerse}
        Our Scottish friend still dressed in kilt continued down the street\\*%
        He hadn't gone ten yards or more when a girl he chanced to meet\\*%
        She said I heard what's under there. Tell me is it so?\\*%
        He said just slip your hand up miss if you'd really like to know
    \end{SongVerse}
    \begin{SongVerse}
        Ring-ding diddle-iddle-i-dee-o, Ring di diddle-i-o\\*%
        He said just slip your hand up miss if you would like to know
    \end{SongVerse}
    \begin{SongVerse}
        She put her hand right up his kilt and much to her surprise\\*%
        The Scotsman smiled and a very strange look came into his eyes\\*%
        She cried why sir that’s gruesome and then she heard him roar\\*%
        If you put your hand up once again, you'll find it's grew some more.
    \end{SongVerse}
    \begin{SongVerse}
        Ring-ding diddle-iddle-i-dee-o, Ring di diddle-i-o\\*%
        If you put your hand up once again, you'll find it's grew some more.
    \end{SongVerse}
\end{SongText}
